---
title: "Shape congruence of population, genetic, and environmental network topologies."
description: |
  Networks structures are common features in ecological and environmental anlyses because they conceptually fit into notions of connectivity and information flows between populations or across landscapes.
author:
  - name: Rodney J. Dyer
    url: https://dyerlab.org
    affiliation: Center for Environmental Studies<br>Virginia Commonwealth University<br>&nbsp;
    affiliation_url: https://ces.vcu.edu
    orcid_id: 0000-0003-4707-3453
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gstudio)
library(popgraph)
library(tidyverse)
```




This manuscript introduces several measures that can be used to quantify similarity in network structures commonly found in ecological and environmental research.

With the goal of stimulating the development of new, and hopefully more effective, solutions we begin by considering some of the problems associated with topological comparisons.

- Localized versus Global 

- Search


One of the main challenges to 


## Methods

The underlying generative functions that create connected topologies 




```{r echo=FALSE}

```








## Localized similarities



### Connection Similarity

*Degree Correlation*


### Neighborhood Similarity

*Clique size Correlation* 



## Global Similarities


### Connectivity Similarity



What is the distribution of connectivity values that produce a sturcture like this?



### Structural Congruence

Are the edges in $G_1$ connected to the same set of edges in $G_2$?





### Distance Congruence

Independent of how the network is configured, are the relative distances between nodes in the network correlated.






## Example Human 






